Stock forecasting algorithms and their usage

### 2015-06-12 Paper_self.tex
list of figures
Final Paper Version

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
\usepackage[]{blindtext, graphicx}
\usepackage[hidelinks]{hyperref}
\graphicspath{ {Figures/} }
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{color}

@@

\begin{abstract}
%\boldmath
In this paper, we propose several methods to predict future stock prices. There are
a lot of algorithms out there but some are more reliable than others. As expected,
in most cases the general rule: \textit{"the more complex, the better the prediction" } is true.
However there are some relatively easy algorithms than can predict the stock prices of the future quite well.
We are going to present and analyse some of these algorithms and take a deeper look into them.
Just to make this clear, there is not a single algorithm, than can predict the future of a 
stock 100\% correctly. The relationships of the global stock market are to complex to bring them down in a 
single computer program. We will show the experimental results we got with several algorithms and compare them.
Also we will take a short look into investment strategies based on these forecasts and take a look at the results.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
stock, forecast, prediction, paper, algorithms, neuronal-network.
\end{IEEEkeywords}

@@

One very important thing is to observe the international newscasts. If the global economy, or even the economy of a single country is experiencing a financial crisis, the stock market will follow that trend. But those trends are most likely to be relatively slow and easy to predict even looking at the stock prices itself. What is more dangerous are catastrophes. After a catastrophe there is often a low point on the stock market. This low point comes so fast, that only algorithms that observe the news have a chance to prevent huge losses.

@@

We used yahoo finance because it gives easy access to numerous stocks and their historical prices. The API yahoo grants is pretty simple. The only thing you have to do to download the data you need is, preparing a link so it fits your needs. For example the url -

@@

We implemented three different algorithms to predict stock prices and maximise the outcome. All three of them only consider one stock at a time and do not take any global news or trends in account. In this section describes the algorithms used in detail

@@

To get better and more reliable results, we did not test this method on single stocks. We wanted to get a big amount of predictions and see whether they were good. Because if you only predict one single price it is not really significant, but if you predict many prices and take the average of these predictions you get meaningful results. That is why we took 150 stocks for our algorithm to predict. We tested 3 sets of data with 150 stocks each.

@@

\begin{figure}[!h]
  \includegraphics{MSFT_MA}
  \caption{Moving Average of MSFT (Microsoft Corporation)}
  \label{fig:MSFT_MA}
\end{figure}

@@

We now take a closer look at a single passage of the stock to explain our approach in more detail.

\begin{figure}[!h]
  \includegraphics{MSFT_Zoomed}
  \caption{MSFT stock zoomed}
  \label{fig:MSFT_Z}
\end{figure}

@@

The conclusion of this paper is, that you can get pretty good results in forecasting stock prices and try to get profit out of the stock market even with algorithms that do not consider the global news. However the stock market is pretty fragile and fast-paced, so while you are trying to make profit, it is always a possibility that the exact opposite happens. But with the right algorithms it can be worth the risk of investing into the market.

@@

We implemented good working algorithms that can predict the stock price. But if these algorithms would take the global news into account there prediction could be better. With our algorithms we can never have a perfect result because if something global happens that affects the stock market, our algorithms are not fast enough to react and sell all stocks we bought. So the addition of a newscrawler would be a good idea for future work because it would help making the algorithms even more reliable in unforeseeable circumstances.

@@

% use section* for acknowledgement
\section*{Acknowledgment}

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
\usepackage[]{blindtext, graphicx}
\usepackage[hidelinks]{hyperref}
\graphicspath{ {Figures/} }
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{color}
\usepackage{fancyhdr}
\pagestyle{plain}

@@

\begin{abstract}
%\boldmath
In this paper, we propose several methods to predict future stock prices. There are
a lot of algorithms out there but some are more reliable then others. As expected,
in most cases the general rule: \textit{"the more complex, the better the prediction" } is true.
However there are some relatively easy algorithms that can predict the stock prices of the future quite well.
We are going to present and analyse some of these algorithms and take a deeper look into them.
Just to make this clear, there is not a single algorithm, that can predict the future of a 
stock 100\% correctly. The relationships of the global stock market are to complex to bring them down in a 
single computer program. We will show the experimental results we got with several algorithms and compare them.
Also we will take a short look into investment strategies based on these forecasts and take a look at the results.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
stock, forecast, prediction, paper, algorithms.
\end{IEEEkeywords}

@@

One very important thing is to observe the international newscasts. If the global economy, or even the economy of a single country is experiencing a financial crisis, the stock market will follow that trend. But those trends are most likely to be relatively slow and easy to predict even looking at the stock prices itself. The thing that is more dangerous are catastrophes. After a catastrophe there is often a low point on the stock market. This low point comes so fast, that only algorithms that observe the news have a chance to prevent huge losses.

@@

We used yahoo finance because it gives easy access to numerous stocks and their historical prices. The usage of the API yahoo grants is pretty simple. The only thing you have to do to download the data you need is, preparing a link so it fits your needs. For example the url -

@@

We implemented three different algorithms to predict stock prices and maximise the outcome. All three of them only consider one stock at a time and do not take any global news or trends in account. In this section we describe the algorithms we used in more detail.

@@

To get better and more reliable results, we did not test this method on single stocks. We wanted to get a big amount of predictions and see whether they were good. If you only predict one single price it is not really significant, but if you predict many prices and take the average of these predictions you get meaningful results. That is why we took 150 stocks for our algorithm to predict. We tested 3 sets of data with 150 stocks each.

@@

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{MSFT_MA}
	\caption{Moving Average of MSFT (Microsoft Corporation)}
	\label{fig:MSFT_MA}
\end{figure}

@@

We now take a closer look at a single passage of the stock to explain our approach in more detail.
\\

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{MSFT_Zoomed}
	\caption{Detailed Moving Average of MSFT}
	\label{fig:MSFT_Z}
\end{figure}

@@

The conclusion of this paper is, that you can get good results in forecasting stock prices and try to get profit out of the stock market even with algorithms that do not consider the global news. However the stock market is pretty fragile and fast-paced, so while you are trying to make profit, it is always a possibility that the exact opposite happens. But with the right algorithms it can be worth the risk of investing into the market.

@@

We implemented good working algorithms that can predict the stock price. But if these algorithms would take the global news into account their prediction could be better. With our algorithms we can never have a perfect result because if something global happens that affects the stock market, our algorithms are not fast enough to react and sell all stocks we bought. So the addition of a newscrawler would be a good idea for future work because it would help making the algorithms even more reliable in unforeseeable circumstances.

@@

\listoffigures
% use section* for acknowledgement
\section*{Acknowledgment}
